\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards \vspace{-2ex} \versionline{14}

### 2016-02-05 ICRA2016/bandits_docs/includes/problem_statement.tex
Made first round of ICRA revisions, v14 of the paper

We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability of force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
We assume the nominal object shape is given as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within. 
The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
We assume soft-finger contacts with a Coulomb friction model~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.

\subsection{Grasp and Object Parameterization}
\seclabel{grasp-param}
The grasp parameters are illustrated in~\figref{grasp-model}.
Let $\bg = (\bx, \bv)$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
%Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$, and specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
Let $\mG = \{ (\bx, \bv) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mA\}$ denote the space of all objects, where $\mA$ is the space of all SDFs for closed and compact surfaces.
We denote by $\mM = \mG \times \mH$ the Grasp Moduli Space of all parallel-jaw grasps and objects~\cite{pokorny2013grasp}.

@@

\subsection{Sources of Uncertainty}
\seclabel{uncertainty}
We assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification material properties, respectively. 
We denote by $\mN(\mu,\Sigma)$ a Gaussian distribution with mean $\mu$ and variance $\Sigma$.
Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$~\cite{barfoot2014associating}.
Let $\nu \sim \mN\left(\mathbf{0}, \Sigma_{\nu}\right)$ denote zero-mean Gaussian gripper pose uncertainty with mean $\mu_{\nu} \in \mG$.
Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of the random variables.

\subsection{Contact Model}
\seclabel{contact}
Given a grasp $\bg$ on an object $\mO$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface as shown in \figref{grasp-model}.
Each contact $\bc_i = \bx + (-1)^{i} (w / 2 - t_i^*) \bv$ where~\cite{mahler2015gp}:
%\vspace{-1ex}
\begin{align*}
	t_i^* &= \myargmin{t \geq 0} t \text{ such that } f\left(\bx +  (-1)^{i} (w / 2 - t) \bv\right) = 0.
\end{align*}
\noindent Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tangent vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
To compute the forces that each contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013c} into a set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
Each force $\bbf_{i,j} \in \mF_{i}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.
Under the soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
Thus the set of all contact wrenches that can be applied by a grasp $\bg$ under the model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.

\subsection{Quality Metric}
\seclabel{quality}
In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as the quality metric.
$P_F$ has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose} and is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data.

Let $F \in \{0, 1\}$ denote the occurrence of force closure.
For a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.

\subsection{Objective}
We are interested in finding a grasp $\bg^*$ that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
Since the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

>>>>

We consider the problem of planning a grasp that maximizes an expected binary quality metric, such as the probability of force closure ($P_F$), for a given 3D object model and parallel-jaw grippers under uncertainty in object pose, gripper pose, and friction coefficient in as few samples as possible.
%We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability of force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
We assume the nominal object shape is given as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within. 
The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
We assume soft-finger contacts with a Coulomb friction model~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.

\subsection{Grasp and Object Parameterization}
\seclabel{grasp-param}
The grasp parameters are illustrated in~\figref{grasp-model}.
Let $\bg = (\bx, \bv)$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
%Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object for SDF $f$.
We specify all points with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.

@@

\subsection{Objective}
Our objective is to find grasp $\bg^*$ that maximizes the probability of success $P_S(\bg))$ for a binary grasp quality metric $S(\bg) \in \{0, 1\}$ such as force closure~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to uncertainty in the state of the object, environment, or robot.
Since sampling in high-dimensional spaces can be computationally expensive, we attempt to solve for $\bg^*$ in as few samples $T$ as possible by maximizing over the sum of $P_S(\bg_t)$ for grasps sampled at times $t=1, ..., T$~\cite{laskey2015bandits, srinivas10gaussian}:
%\vspace{-2ex}
\begin{align*}
	\underset{\bg_1, .., \bg_T \in \mG}{\text{maximum }} {\textstyle \sum_{t=1}^T \nolimits } P_S(\bg_t). \label{eq:obj}
\end{align*}

Since maximizing over a high-dimensional continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating and ranking a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ using Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

\subsection{Quality Metric}
\seclabel{quality}
In this work we use the probability of force closure ($P_F$), or the ability to resist external force and torques in arbitrary directions~\cite{mahler2015gp}, as the quality metric.
$P_F$ is relatively inexpensive to evaluate, allowing us to better study the effects of large amounts of data on convergence of Equation~\ref{eq:obj}, and has shown some promise in physical experiments~\cite{kim2012physically, weisz2012pose}.

Let $F \in \{0, 1\}$ denote the occurrence of force closure.
For a grasp $\bg$ on object $\mO$ under uncertainty in object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$ the probability of force closure $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$, 
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute a set of possible contact wrenches $\mW$ using a soft finger contact model~\cite{zheng2005}.
Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.

\subsection{Sources of Uncertainty}
\seclabel{uncertainty}
For $P_F$ evaluation we assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification of material properties. 
Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be the mean object pose.
We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$~\cite{barfoot2014associating}.
Let $\nu \sim \mN\left(\mathbf{0}, \Sigma_{\nu}\right)$ denote zero-mean Gaussian gripper pose uncertainty with mean $\mu_{\nu} \in \mG$.
Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of the random variables.

\subsection{Contact Model}
\seclabel{contact}
Given a grasp $\bg$ on object surface $f$ and samples $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$, let $\bc_i \in \mathbb{R}^3$ denote the 3D contact location between the $i$-th jaw and surface as shown in \figref{grasp-model}.
Let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal and let $\bt_{i,1}, \bt_{i,2} \in \bS^2$ be its tangent vectors.
To compute the forces that each soft contact can apply to the object for friction coefficient $\hat{\gamma}$, we discretize the friction cone at $\bc_i$~\cite{pokorny2013c} into a set of $l$ facets with vertices $\mF_{i} = \left\{ \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \big| j = 1, ..., l \right\}$.
Thus the set of wrenches that $\bg$ can apply to $\mO$ is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \bbf_{i,j} \times \rho_i) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at $\bc_i$.

### 2016-02-05 ICRA2016/bandits_docs/includes/related_work.tex
Made first round of ICRA revisions, v14 of the paper

Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric~\cite{pokorny2013c}.
Usually it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
Robust grasp planning considers the same problem in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
One way to treat perturbations is statistical sampling.
Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasp computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt! stochastic sampling-based grasp planner.
%This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic wrench space metrics.
Brook et al.~\cite{brook2011collaborative} planned robust grasps for a database of 892 point clouds and developed a model to predict grasp success on a physical robot based on correlations with grasps in the database.   
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.

Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps from human demonstrators~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances, each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
We estimate $P_F$ using similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.

Our work is also closely related to research on actively sampling grasps to build a statistical model of grasp quality from fewer examples~\cite{detry2011learning, kroemer2010combining, salganicoff1996active}.
%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high $P_F$.

>>>>

Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric, such as the epsilon quality~\cite{pokorny2013c}, correlation with human labels~\cite{balasubramanian2012physical, kappler2015leveraging}, or success in physical trials.
Often it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
As computing quality metrics can be time consuming, recent work has explored how a robust grasp computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt! stochastic sampling-based grasp planner.

Robust grasp planning considers optimizing a grasp quality metric in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
One way to perturbations is statistical sampling.
Since sampling in high dimensions can be computationally demanding, recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic wrench space metrics.
Brook et al.~\cite{brook2011collaborative} planned robust grasps for a database of 892 point clouds and developed a model to predict grasp success on a physical robot based on correlations with grasps in the database.   
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.

Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps from human demonstrators~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances, each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
In comparison, we estimate $P_F$ given a known 3D object model from similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.

Our work is also closely related to research on actively sampling grasps to build a statistical model of grasp quality from fewer examples~\cite{detry2011learning, kroemer2010combining, salganicoff1996active}.
%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Pinto et al.~\cite{pinto2016supersizing} used importance sampling over grasp success probabilities predicted from images by a Convolutional Neural Network to actively acquire over 700 hours of labels for successful and unsuccessful grasps.
Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
%Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the MAB model of~\cite{laskey2015bandits} from 2D to 3D and study the scaling effects of using prior data from Dex-Net on the rate of convergence to a grasp with high $P_F$.

### 2016-02-05 ICRA2016/bandits_docs/paper.tex
Made first round of ICRA revisions, v14 of the paper

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards
	\vspace{-2ex}
	\versionline{11}}
\author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^{1}$
%\vspace{-2ex}
\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, ftpokorny, brian.hou, goldberg\}@berkeley.edu, melrose\_roderick@brown.edu}}}%
%\thanks{$^2$IEOR Dept; {\tt\small goldberg@berkeley.edu}}%
%\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{{\small $^2$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}}%
\thanks{{\small $^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}} }
}
\maketitle

@@

\section{Acknowledgments}
{\small
This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahaana Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
}

>>>>

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards
	\vspace{-2ex}
	\versionline{14}}
\author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^{1}$
%\vspace{-2ex}
\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, ftpokorny, brian.hou, goldberg\}@berkeley.edu, melrose\_roderick@brown.edu}}}%
%\thanks{$^2$IEOR Dept; {\tt\small goldberg@berkeley.edu}}%
%\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{{\small $^2$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}}%
\thanks{{\small $^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}} }
}
\maketitle

@@

\section{Acknowledgments}
{\small
This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab; and by the Department of Defense (DoD) through the National Defense Science \& Engineering Graduate Fellowship (NDSEG) Program.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahaana Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
}
